---
title: "Working File"
output:
  rmarkdown::html_vignette:
    toc: true
vignette: >
  %\VignetteIndexEntry{Working File}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r load_libraries, include = FALSE}
library(tidyverse)
library(readr)
library(ggplot2)
library(shinipsum)
library(fakir)
library(usethis)
library(jsonlite)
library(httr)
library(lubridate)
library(kableExtra)
```

# Nutrition Analysis: Shiny Dashboard
## Overview


## Data Sources
The possible ways to add ingredients to your personal dashboard are as follows:  
   1. Food Data Central (FDC)
   2. Manual Entry

### Food Data Central
"The USDA National Nutrient Database for Standard Reference is a database produced by the United States Department of Agriculture that provides the nutritional content of many generic and proprietary-branded foods. Released in August 2015 and revised in May 2016, the current release, Standard Reference 28 (SR28), contains "data on 8,800 food items and up to 150 food components".[1] New releases occur about once per year. The database may be searched online,[2] queried through a representational state transfer API,[3] or downloaded"  - Wikipedia

Being able to browse through food items will be a main component of the Shiny project.  To get this data, the user will be able to enter an API-token and a search term to return a list of items to add to their library.  

Current nutrients listed in the FDC database:  
```{r nutrients, echo = FALSE, warning = FALSE}
# Each Set
fdc_branded <- 
  fdc_search(api_key = "",
           search_term = "Chicken Broth Target Stores",
           page_size = 100,
           type = "Branded")

fdc_measured <- 
  fdc_search(api_key = "",
           search_term = "Chicken",
           page_size = 100,
           type = "General")
  
nutrients_branded <- 
  fdc_branded %>% 
  distinct(nutrient_name, nutrient_id) %>% 
  select(nutrient_name, nutrient_id) %>% 
  arrange(nutrient_name, nutrient_id)

nutrients_measured <- 
  fdc_measured %>% 
  distinct(nutrient_name, nutrient_id) %>% 
  select(nutrient_name, nutrient_id)

nutrient_id_used <- 
  tibble(nutrient_id = c(1008, 1003, 1005, 1257, 1258)) %>% 
  mutate(order = 1:nrow(.))

# Joined
nutrients <- 
  nutrients_branded %>% 
  mutate(source = "Branded") %>% 
  bind_rows(nutrients_measured %>% 
              mutate(source = "Measured")) %>% 
  mutate(listed = "X") %>% 
  group_by(nutrient_name, nutrient_id) %>% 
  spread(key = source, value = listed) %>% 
  ungroup() %>% 
  left_join(nutrient_id_used %>% 
              mutate(used = "X"),
            by = "nutrient_id") %>% 
  arrange(order, nutrient_name, nutrient_id) %>% 
  select(-order)
  

# Output
nutrients %>% 
  mutate(across(.cols = Branded:used,
                ~case_when(
                  . == "X" ~ .,
                  TRUE ~ ""))) %>% 
  titler() %>% 
  kbl() %>% 
  kable_styling()
```



# Sandbox ====
```{r sandbox, include = FALSE, }
fdc_branded %>% 
  filter(nutrient_id %in% nutrient_id_used$nutrient_id) %>% 
  mutate(nutrient = case_when(
           nutrient_id == 1008 ~ "Calories (KCal)",
           nutrient_id == 1003 ~ "Protein (g)",
           nutrient_id == 1005 ~ "Carbohydates (g)",
           nutrient_id == 1257 ~ "Fats (trans)",
           nutrient_id == 1258 ~ "Fats (saturated)"),
         nutrient = factor(nutrient, 
                           levels = c("Calories (KCal)", 
                                      "Protein (g)", 
                                      "Carbohydates (g)",
                                      "Fats (trans)", 
                                      "Fats (saturated)"))) %>%  
  select(description,
         fdc_id,
         food_category,
         data_type,
         upc = gtin_upc,
         brand_owner,
         brand_name,
         serving_size_unit,
         serving_size,
         nutrient,
         value) %>% 
  spread(key = nutrient, 
         value = value, 
         fill = 0) %>% 
  titler() %>% 
  kbl() %>% 
  kable_styling()

fdc_measured %>% 
  filter(nutrient_id %in% nutrient_id_used$nutrient_id) %>% 
    mutate(nutrient = case_when(
           nutrient_id == 1008 ~ "Calories (KCal)",
           nutrient_id == 1003 ~ "Protein (g)",
           nutrient_id == 1005 ~ "Carbohydates (g)",
           nutrient_id == 1257 ~ "Fats (trans)",
           nutrient_id == 1258 ~ "Fats (saturated)"),
         nutrient = factor(nutrient, 
                           levels = c("Calories (KCal)", 
                                      "Protein (g)", 
                                      "Carbohydates (g)",
                                      "Fats (trans)", 
                                      "Fats (saturated)"))) %>% 
  select(description,
         fdc_id,
         data_type,
         brand_owner,
         brand_name,
         serving_size_unit,
         serving_size,
         nutrient,
         value)
  

```




